---
title: "Compare CpG oe header and join outputs"
output: 
  html_document:
    df_print: paged
    code_folding: hide
    theme: cerulean
    highlight: tango
    toc: true
    toc_depth: 4
    toc_float: true
  word_document: default
editor_options:
  chunk_output_type: inline
---

## Load libraries
```{r}
library(arsenal)
```

## Read in data
```{r}
new_output <- read.csv("/Volumes/web/metacarcinus/Cvirginica/FROGER/20190225_cpg_oe/ID_CpG_labelled_all", sep = "\t", header = TRUE, stringsAsFactors = FALSE)

sam_output <- read.csv("/Volumes/web/metacarcinus/Cvirginica/FROGER/20190225_cpg_oe/ID_CpG_labelled_all.tab", sep = "\t", header = TRUE, stringsAsFactors = FALSE)
```

## preview data frames
```{r}
head(new_output)
head(sam_output)
```

## Show differences between data frames
```{r}
summary(comparedf(new_output, sam_output, by = "ID"))
```

## confirm data frames are not identical 
```{r}
identical(new_output, sam_output)
```


## reorder columns so they are alphabetical
```{r}
colnames(new_output)
```

```{r}
new_order <- data.frame(new_output[,-1])
new_order <- new_order[,order(names(new_order))]
new_output <- cbind(new_output[,"ID"], new_order)
colnames(new_output)[1] <- "ID"
```

```{r}
sam_order <- data.frame(sam_output[,-1])
sam_order <- sam_order[,order(names(sam_order))]
sam_output <- cbind(sam_output[,"ID"], sam_order)
colnames(sam_output)[1] <- "ID"
colnames(sam_output) <- gsub("\\.","_", colnames(sam_output))

```

## Check column names are the same
```{r}
colnames(new_output)
```

```{r}
colnames(sam_output)
```

## See if data frames are identical
```{r}
identical(new_output, sam_output)
```
## Show differences between data frames
```{r}
summary(comparedf(new_output, sam_output, by = "ID"))
```

## There are still a couple differences in the column names
## Change column names to match

```{r}
colnames(sam_output[,32:37])
colnames(new_output[,32:37])

colnames(sam_output)[32:37] <- colnames(new_output)[32:37]

```

```{r}
colnames(sam_output)[47]
colnames(new_output)[47]

colnames(sam_output)[47] <- colnames(new_output)[47]
```


## See if data frames are identical
```{r}
identical(new_output, sam_output)
```

## Show differences between data frames
```{r}
summary(comparedf(new_output, sam_output, by = "ID"))
```

## After ordering columns the same way and making column names consistent, tables show the exact same data confirming nothing weird happened when joining files using the new script